Discriminative Sensing Based on Signal Processing for Information Security Analysis

### 2017-11-08 docs/thesis/chapters/1_introduction/introduction.tex
justificatives and problem statement

Traditionally, cyber defense methods can be effective against ordinary and conventional types of attacks, yet may fail against innovative malicious techniques \cite{lakhina2005mining}. In order to be able to detect and avoid novel attacks and their variations, it is necessary to develop or improve techniques to achieve efficiency on resource consumption, processing capacity and response time. Moreover, it is crucial to obtain high detection accuracy and capacity to detect variations of malicious patterns. Recently, signal processing schemes have being applied to the detection of malicious traffic in computer networks \cite{Lu2009,Huang2009,Zonglin2009,david2011blind,da2012improved,tenorio2013greatest}, showing advances in network traffic analysis.

@@

Cloud computing is a new rapidly evolving paradigm in the world of distributed networking and computation. The basic features of the cloud environment is providing the elastic, on-demand and secure services for the end-users. While the first two requirements are rather well conceptualized and supported by the majority of the cloud platforms in use, security is a serious concern of the cloud providers and governmental organizations as well as academia and research community \cite{csa2016,higashi2015,gartner2015}. Although for the small and medium-sized enterprises (SME) the cloud environment is often the most cost-effective and easily scalable solution, the security and privacy of the sensitive data in cloud platforms are also not fully conceptualized leading to obscure and incomplete security paradigms and solutions.

Additional security issues and requirements have to be considered when mobile clients are actively used in corporate cloud environment \cite{yovel2014}. Today more and more organizations and enterprises are functioning in the Bring-Your-Own-Device (BYOD) paradigm. The uncontrolled usage of the mobile devices represents a serious risk to the development of secure SME cloud platforms being the bottleneck of the corporate information security system (ISS). While the enterprise cloud infrastructure based on the web interface can be protected by powerful third-party services, the corporate mobile client is usually light-weighted and generally less protected.

@@

The field of Mobile Money Transfer (MMT) is a growing market segment and has been motivating investiments into security defense and fraud detection. Obtaining access to data sets of mobile transactions for research is a very hard task due to the intrinsic private nature of such transactions. Scientists and researchers must today spend time and effort in obtaining permits and access to relevant data sets before they can research on such data set. However, PaySim is a financial simulator that simulates mobile money transactions based on an original dataset and provides a synthetic dataset as an approach to such a problem.\footnote{https://www.kaggle.com/ntnu-testimon/paysim1}

Despite the actual high availability of information, the relevant information of some observations is generally of under much reduced dimensionality compared to available data sets. The extraction of relevant information by identifying the generating causes within classes of signals is useful for classification problems and for security analysis. Big data analytics require techniques to deal with multidimensional data, making sense of strucutre and relationship of many dimensions.

Dictionary learning is a signal processing technique based on the principle that some observations can be described by a sparse subset of atoms taken from a redundant dictionary, which represents the causes of some observations of the world. Dictionary Learning is a signal processing technique for sparse representation of signals as basis vectors, learning the representations from training data, as dictionaries. The sparse representation in terms of such dictionaries has attracted increased interest for compressive sensing and for solving problems such as denoising, compression, image processing, data decomposition, feature extraction and classification \cite{tosic2011dictionary, zhang2010discriminative, zhu2016coupled,ravishankar2011mr}.

Tensor decomposition has been adopted for multidimensional data analysis and can be explored for dictionary learning...principalmente por tensor decompositio extrair mais informações e relacionamentos que técnicas tradicionais, podendo ser melhores que técnicas tradicionais de dictionary learning

Iterative dictionary learning has been used as a blind technique for feature extraction, improving classification without require feature selection or principal conponent analysis

We propose methods for information security analysis

Observing the above described landscape, this thesis outlines the concept of the offline mobile cloud security.

Compressive sensing is emergent for signal processing and has been applied to fields such as signal restoration, image processing and classification (sparce representation classification src )

Adaptive techniques for high dimensional and high thoughput

% There are two major approaches for dictionary learning. First is the analytic approach, in which DCT bases, wavelets, curvelets and other nonadaptive functions are used as atoms to construct the dictionaries. Second is the learning-based approaches, such as the unsupervised learning for dictionary construction [9] and the online dictionary learning [11], [10], which use machine learning methods to construct the dictionary. In the analytic approach, some pre-defined functions are used to construct the dictionary. Curvelets [24], which tracks the shape of the discontinuity set, offers efficient and near-optimal representation of smooth objects. Shearlets [25], which is obtained from dilations, action of translations and shear transformations, has nice geometric properties and mathematical properties for image representation. Bandelets [26], which specifies the geometry as a vector field, is de-signed to improve the image compression and noise reduction performance. In the learning-based approach, machine learning methods are used to construct the dictionary from the training data. The least square error is used by the method of the optimal directions (MOD) [27] to update the dictionary iteratively:
% Dictionaries are either available analytically, or can be learned from a suitable training set. While analytic dictionaries permit to capture the global structure of a signal and allow a fast implementation, learned dictionaries often perform better in applications as they are more adapted to the considered class of signals.

In some applications the data and its dictionary are multidimensional, e.g., when estimating jointly behavior of users in social networks. Computing tensor decompositions of multi-way datasets is particularly useful to extract hidden patterns and structure in multidimensional data analytics problems \cite{kolda2009tensor}. Tensor-based algorithms for dictionary learning can improve the performance for cases of multidimensional and separable data, regarding the dictionary identification rating, the required number of training samples and iterations for the optimization problem \cite{roemer2014tensor}.

% In imagery, the numerical burden for (i) learning a dictionary and for (ii) employing the dictionary for reconstruction tasks only allows to deal with relatively small image patches that only capture local image information. Separable dictionaries aims at overcoming these drawbacks by allowing a separable structure on the dictionary throughout the learning process. On the one hand, this permits larger patch-sizes for the learning phase, on the other hand, the dictionary is applied efficiently in reconstruction tasks. The crucial idea is to allow the dictionary to have a separable structure, where separable means that the dictionary D is given by the Kronecker product of two smaller dictionaries A ∈ R h×a and B ∈ R w×b
% Without loss of generality we choose square image patches with w = h = 8, which is in accordance to the patch-sizes mostly used in the literature

Multidimensional parameter estimation and learning multidimensional separable dictionaries are growing research problems. Roemer \emph{et al.} \cite{roemer2014tensor} show that the multidimensional dictionary estimation problem can be efficiently formulated in terms of tensors, and that their results outperform existing schemes by exploiting the multilinear structure of the problem.

Existing dictionary learning schemes can be applied to multidimensional analysis and obtain valuable results. However, the performance of tensor-based algorithms for recovering of a known separable dictionary outperform existing schemes when dealing with growing multidimensional datasets, as can be seen in Figures \ref{fig:fig1} and \ref{fig:fig2}, which show that the recovering rating of traditional algorithms decreases over the dataset increasing.

Figures \ref{fig:fig1} and \ref{fig:fig2} show the evaluation of tensor-based and traditional dictionary learning algorithms for dictionary reconstruction of a multidimensional and separable data. Figure \ref{fig:fig1} presents the results for dictionary reconstruction from a matrix of 1000 elements by 50 atoms, while Figures \ref{fig:fig2} presents the results from a matrix with 24000 entries by 300 atoms. It is possible to observe better reconstruction rating for tensor-based algorithms.

Imbalanced data...
Recent developments in science and technology have enabled the growth and availability of raw data to occur at an explosive rate. This has created an immense opportunity for knowledge discovery and data engineering research to play an essential role in a wide range of applications from daily civilian life to national security. However, the high availability of raw data increases the challenges related to big data analytics and to imbalanced data, which corresponds to data sets exhibiting significant imbalances of classes or rare events of some classes. The fundamental issue with the imbalanced learning problem is the ability of imbalanced data to significantly compromise the performance of most standard learning algorithms

A key challenge to use sparse coding and dictionary learning for classification is how to find proper dictionaries and coefficients that highligh discriminative structure and relationships of one dataset. Therefore, we introduce a tensor-based dictionary learning method for fraud detecton from unbalanced data. Specifically, we apply a sparse representation based classification (SRC) method through learning a tensor-based dictionary and evaluate the reconstruction error for fraud classification. In this paper, we propose a tensor-based sparse representation and dictionary learning technique to analyze mobile money transactions in order to identify frauds. We propose to use tensor-based dictionary learning for learning fraudulent and legitimante data separetelly, and apply the learned dictionaries to reconstruct a test signal and classify it as fraud or ligitimate, according to the minimum reconstruction error measured by some metrics.

%However, tensor-based algorithms face challenges to achieve reasonable processing time to handle large-scale tensor factorizations \cite{de2014distributed}, demanding efforts in order to explore distributed processing techniques for tensor-based analytics of large datasets. We propose a distributed and tensor-based approach for multidimensional dictionary learning in order to obtain better processing time for larger datasets. We focus on a distributed implementation of T-MOD \cite{roemer2014tensor} algorithm, based on a modification of Almeida and Kibangou's \cite{de2014distributed} approach to use Tucker-2 decomposition. We perform experiments to test different methods for learning dictionaries, evaluating the processing time and the reconstruction of a dictionary of multidimensional and separable data.

@@

In the context of anomaly-based schemes, this thesis proposes a statistical approach based on signal processing techniques for the detection of malicious traffic in computer networks. Inspired by \cite{david2011blind,da2012improved}, this thesis models the network traffic using a signal processing formulation as a composition of three components: legitimate traffic, malicious traffic and noise, taking into account the incoming and outgoing traffic in certain types of network ports (TCP or UDP). The proposed technique is based on eigenvalue analysis, model order selection (MOS) and similarity analysis. In contrast to \cite{david2011blind,da2012improved,tenorio2013greatest}, MOS and eigenvalue analysis are applied to detect time frames under attack. In addition, we also evaluate the accuracy and performance of the proposed framework applied to a experimental scenario and to the DARPA 1998 dataset \citep{osanaiye2016distributed}, which is a well known network traffic dataset. Furthermore, this proposed approach has its accuracy evaluation based on eigen similarity analysis for extracting detailed information about accurate time and network ports under attack.

This thesis also proposes a novel approach based on user behavior analysis through Model Order Selection (MOS) \cite{tenorio2013greatest}, in order to detect possible threats, and to reduce the risks and the harm of the most common threats, which are the expired user misusing password and the intruder attack. Additionally, the behavioral analysis can indicate well known malicious behaviors, their variations, as well as novel attacks, which present low or high variance in comparison to legitimate user behaviors. The main target of this proposed solution is to provide a maximum defense at the minimal resource cost.

Finally, we propose a fraud detection system for mobile payment transactions... we propose to apply the tensor deconposition for dictionary learning in order to evidentiate the discriminative sensing of a fraud detection dataset.

@@

>>>>

Traditionally, cyber defense methods can be effective against ordinary and conventional types of attacks, yet may fail against innovative malicious techniques \cite{lakhina2005mining}. In order to be able to detect and avoid novel attacks and their variations, it is necessary to develop or improve techniques to achieve efficiency on resource consumption, processing capacity and response time. Moreover, it is crucial to obtain high detection accuracy and capacity to detect variations of malicious patterns. Recently, signal processing schemes have being applied to detect malicious traffic in computer networks \cite{Lu2009,Huang2009,Zonglin2009,david2011blind,da2012improved,tenorio2013greatest, vieira2017model}, showing advances in network traffic analysis.

@@

Cloud computing is a new rapidly evolving paradigm in the world of distributed networking and computation. The basic features of the cloud environment is providing elastic, on-demand and secure services for the end-users. While the first two requirements are rather well conceptualized and supported by the majority of the cloud platforms in use, security is a serious concern of the cloud providers and governmental organizations as well as academia and research community \cite{csa2016,higashi2015,gartner2015}. Although for the small and medium-sized enterprises (SME) the cloud environment is often the most cost-effective and easily scalable solution, the security and privacy of the sensitive data in cloud platforms are also not fully conceptualized leading to obscure and incomplete security paradigms and solutions.

Additional security issues and requirements have to be considered when mobile clients are actively used in corporate cloud environment \cite{yovel2014}. Today organizations and enterprises are adopting the Bring-Your-Own-Device (BYOD) paradigm. The uncontrolled usage of the mobile devices represents a serious risk to the development of secure SME cloud platforms being the bottleneck of the corporate information security system (ISS). While the enterprise cloud infrastructure based on the web interface can be protected by powerful third-party services, the corporate mobile client is usually light-weighted and generally less protected.

@@

The field of Mobile Money Transfer (MMT) is a growing market segment and has been motivating investiments into security defense and fraud detection. Obtaining access to data sets of mobile transactions for research is a very hard task due to the intrinsic private nature of such transactions. Scientists and researchers must today spend time and effort in obtaining access to relevant data sets before they can research on such data set. However, PaySim is a financial simulator that simulates mobile money transactions based on an original dataset and provides a synthetic dataset as an approach to such a problem.\footnote{https://www.kaggle.com/ntnu-testimon/paysim1}

Recent developments in science and technology have enabled the growth and availability of raw data to occur at an explosive rate. This has created an immense opportunity for knowledge discovery and data engineering research to play an essential role in a wide range of applications from daily civilian life to national security. Despite the actual high availability of information, the relevant information of some observations is generally of under much reduced dimensionality compared to available data sets. The extraction of relevant information by identifying the generating causes within classes of signals is useful for classification problems and for security analysis.

The high availability of raw data increases the challenges related to big data analytics and to imbalanced data, which corresponds to data sets exhibiting significant imbalances of classes or rare events of some classes. The fundamental issue with the imbalanced learning problem is the ability of imbalanced data to significantly compromise the performance of most standard learning algorithms. Data analysis of imbalanced data is challenging for classification and prediction problems related to anomaly detection, novelty detection, fraud detection and attack detection. Considering that imbalanced data can be composed by rare or unknown events, adaptive techniques can be useful in order to improve models and be able to react to changes or unknown patterns and maintain acceptable performance for classification algorithms. Adaptive techniques are also important for online data analysis or streaming processing, where an incremental processing approach can be applied to deal with high thoughput data analysis.

Compressed Sensing (CS) aims to obtain the most relevant information of a dataset, what makes it useful for compression, signal reconstruction, image processing and classification, such as in sparce representation classification (SRC) problems. Dictionary learning is related to CS but seeks to obtain compact and meaningful signal representations, known as dictionary, from learning algorithms or models. DL is a signal processing technique for sparse representation of signals as basis vectors, learning the representations from training data, as dictionaries. DL is based on the principle that some observations can be described by a sparse subset of atoms taken from a redundant dictionary, which represents the causes of some observations of the world. The sparse representation in terms of such dictionaries has attracted increased interest for compressive sensing and for solving problems such as denoising, compression, image processing, data decomposition, feature extraction and classification \cite{tosic2011dictionary, zhang2010discriminative, zhu2016coupled,ravishankar2011mr}.

Dictionaries are either available analytically, or can be learned from a suitable training set. DL can be formulated as an adptive algorithm that learns from traning data that is updated to represent changes or to adpat to new patterns. Iterative dictionary learning has been used as a blind technique for feature extraction, improving classification without require feature selection or principal conponent analysis

In some applications, the data and its dictionary are multidimensional, e.g., when estimating jointly behavior of users in social networks. Computing tensor decompositions of multi-way datasets is particularly useful to extract hidden patterns and structure in multidimensional data analytics problems \cite{kolda2009tensor}. Tensor-based algorithms for dictionary learning can improve the performance for cases of multidimensional and separable data, regarding the dictionary identification rating, the required number of training samples and iterations for the optimization problem \cite{roemer2014tensor}. Existing dictionary learning schemes can be applied to multidimensional analysis and obtain valuable results. However, the performance of tensor-based algorithms for recovering of a known separable dictionary outperform existing schemes when dealing with growing multidimensional datasets.

@@

Considering the above described landscape, this thesis outlines the development and evaluation of approaches based on signal processing for information security analysis, through methods to make the data discriminative and able to identify structures, hidden patterns and the most relevant information for network attack detection, mobile malicious behavior analysis and fraud detection in mobile money transactions.

In the context of anomaly-based schemes, this thesis proposes a statistical approach based on signal processing techniques for detection of malicious traffic in computer networks. Inspired by \cite{david2011blind,da2012improved}, this thesis models the network traffic using a signal processing formulation as a composition of three components: legitimate traffic, malicious traffic and noise, taking into account the incoming and outgoing traffic in certain types of network ports (TCP or UDP). The proposed technique is based on eigenvalue analysis, model order selection (MOS) and similarity analysis. In contrast to \cite{david2011blind,da2012improved,tenorio2013greatest}, MOS and eigenvalue analysis are applied to detect time frames under attack. In addition, we also evaluate the accuracy and performance of the proposed framework applied to a experimental scenario and to the DARPA 1998 dataset \citep{osanaiye2016distributed}, which is a well known network traffic dataset. Furthermore, this proposed approach has its accuracy evaluation based on eigen similarity analysis for extracting detailed information about accurate time and network ports under attack.

This thesis also proposes an architecture and approach based on user behavior analysis of mobile apps through Model Order Selection (MOS) \cite{tenorio2013greatest}, in order to detect possible threats, and to reduce the risks and the harm of the most common security threats to corporate mobile apps, which are the expired user misusing password and the intruder attack. Additionally, the behavioral analysis can indicate well known malicious behaviors, their variations, as well as novel attacks, which present low or high variance in comparison to legitimate user behaviors. The main target of this proposed solution is to provide a maximum defense at the minimal resource cost.

Considering that a key challenge to use sparse coding and dictionary learning for classification is how to find proper dictionaries and coefficients that highligh discriminative structure and relationships of one dataset, and also considering that big data problems require techniques to deal with multidimensional data in order to make sense of strucutre and relationship of many dimensions, we also propose a tensor-based dictionary learning method for fraud detecton from unbalanced data, in order to apply the tensor deconposition for dictionary learning methods in order to evidentiate the discriminative sensing of a fraud detection dataset. Specifically, we propose to apply a sparse representation based classification (SRC) method through learning a tensor-based dictionary and evaluate the reconstruction error for fraud classification of mobile money transactions. We propose to use tensor-based dictionary learning for learning fraudulent and legitimante data separetelly, and apply the learned dictionaries to reconstruct a test signal and classify it as fraud or ligitimate, according to the minimum reconstruction error measured by some metrics.

@@

architecture and performance evaluation for mobile behavioral analysis

an adaptive fraud detecion technique for imbalanced data

applied to security analysis, such as network attack detection, malicious behavios in mobile apps and fraud detection in mobile payment transacions

### 2017-11-08 docs/thesis/chapters/4_tensor_dl/tensor_dl.tex
introducion...
conclusion and introduction
justificatives and problem statement

\chapter{Tensor-based Discriminative Sensing for Fraud Detection}
\label{ch:tensor_dl}

@@

% There are two major approaches for dictionary learning. First is the analytic approach, in which DCT bases, wavelets, curvelets and other nonadaptive functions are used as atoms to construct the dictionaries. Second is the learning-based approaches, such as the unsupervised learning for dictionary construction [9] and the online dictionary learning [11], [10], which use machine learning methods to construct the dictionary. In the analytic approach, some pre-defined functions are used to construct the dictionary. Curvelets [24], which tracks the shape of the discontinuity set, offers efficient and near-optimal representation of smooth objects. Shearlets [25], which is obtained from dilations, action of translations and shear transformations, has nice geometric properties and mathematical properties for image representation. Bandelets [26], which specifies the geometry as a vector field, is de-signed to improve the image compression and noise reduction performance. In the learning-based approach, machine learning methods are used to construct the dictionary from the training data. The least square error is used by the method of the optimal directions (MOD) [27] to update the dictionary iteratively:
% Dictionaries are either available analytically, or can be learned from a suitable training set. While analytic dictionaries permit to capture the global structure of a signal and allow a fast implementation, learned dictionaries often perform better in applications as they are more adapted to the considered class of signals.

@@

% In imagery, the numerical burden for (i) learning a dictionary and for (ii) employing the dictionary for reconstruction tasks only allows to deal with relatively small image patches that only capture local image information. Separable dictionaries aims at overcoming these drawbacks by allowing a separable structure on the dictionary throughout the learning process. On the one hand, this permits larger patch-sizes for the learning phase, on the other hand, the dictionary is applied efficiently in reconstruction tasks. The crucial idea is to allow the dictionary to have a separable structure, where separable means that the dictionary D is given by the Kronecker product of two smaller dictionaries A ∈ R h×a and B ∈ R w×b
% Without loss of generality we choose square image patches with w = h = 8, which is in accordance to the patch-sizes mostly used in the literature

@@

\begin{figure}[!htb]
     \centering 
	 \includegraphics[width=0.4\textwidth]{figures/5_20_2000_1000_100.eps}
     \caption{Matrix of 1.000 elements, 2000 sample training, 100 iterations}
     \label{fig:fig1}
\end{figure}

\begin{figure}[!htb]
     \centering 
	 \includegraphics[width=0.4\textwidth]{figures/5_20_2000_24000_100.eps}
     \caption{Matrix of 24.000 elements, 2000 sample training, 100 iterations}
     \label{fig:fig2}
\end{figure}

>>>>

\chapter{Tensor-based Discriminative Sensing for Fraud Detection}
\label{ch:4_tensor_dl}

@@

There are two major approaches for dictionary learning. First is the analytic approach, in which DCT bases, wavelets, curvelets and other nonadaptive functions are used as atoms to construct the dictionaries. Second is the learning-based approaches, such as the unsupervised learning for dictionary construction [9] and the online dictionary learning [11], [10], which use machine learning methods to construct the dictionary. In the analytic approach, some pre-defined functions are used to construct the dictionary. Curvelets [24], which tracks the shape of the discontinuity set, offers efficient and near-optimal representation of smooth objects. Shearlets [25], which is obtained from dilations, action of translations and shear transformations, has nice geometric properties and mathematical properties for image representation. Bandelets [26], which specifies the geometry as a vector field, is de-signed to improve the image compression and noise reduction performance. In the learning-based approach, machine learning methods are used to construct the dictionary from the training data. The least square error is used by the method of the optimal directions (MOD) [27] to update the dictionary iteratively:

Dictionaries are either available analytically, or can be learned from a suitable training set. While analytic dictionaries permit to capture the global structure of a signal and allow a fast implementation, learned dictionaries often perform better in applications as they are more adapted to the considered class of signals.

@@

In imagery, the numerical burden for (i) learning a dictionary and for (ii) employing the dictionary for reconstruction tasks only allows to deal with relatively small image patches that only capture local image information. Separable dictionaries aims at overcoming these drawbacks by allowing a separable structure on the dictionary throughout the learning process. On the one hand, this permits larger patch-sizes for the learning phase, on the other hand, the dictionary is applied efficiently in reconstruction tasks. The crucial idea is to allow the dictionary to have a separable structure, where separable means that the dictionary D is given by the Kronecker product of two smaller dictionaries A ∈ R h×a and B ∈ R w×b

% Without loss of generality we choose square image patches with w = h = 8, which is in accordance to the patch-sizes mostly used in the literature

@@

\begin{figure}[!htb]
     \centering 
	 \includegraphics[width=12cm]{figures/5_20_2000_1000_100.eps}
     \caption{Matrix of 1.000 elements, 2000 sample training, 100 iterations}
     \label{fig:fig1}
\end{figure}

\begin{figure}[!htb]
     \centering 
	 \includegraphics[width=12cm]{figures/5_20_2000_24000_100.eps}
     \caption{Matrix of 24.000 elements, 2000 sample training, 100 iterations}
     \label{fig:fig2}
\end{figure}

### 2017-11-08 docs/thesis/chapters/5_conclusion_future_work/conclusion.tex
justificatives and problem statement

\begin{enumerate}
	\item We proposed an approach based on eigen similarity analysis for extracting detailed information about accurate time and network ports under network attack, and evaluated the accuracy and performance of the proposed framework applied to a experimental scenario and to the DARPA 1998 dataset;
	\item We discussed the computational complexity of the proposed framework and evaluated the required processing time for tested scenarios;
	\item We proposed an architechture and techniques for offline behavioral analysis of a corporate mobile client security architecture;
	\item We discussed the processing time of the proposed framework for mobile devices;
	\item We proposed an tensor-based dictionary learning approach for fraud detection in mobile payment transactions;
	\item We \textbf{published five papers} reporting our results, as follows:
	\begin{enumerate}
		\item T. P. B. Vieira, D. F. Ten\'orio, J. P. C. L. da Costa, E. P. de Freitas, G. Del Galdo, and R. T. de Sousa J\'unior, \textit{Model Order Selection and Eigen Similarity based Framework for Detection and Identication of Network Attacks}. Journal of Networking and Computer Applications (JNCA), Vol 90, Jul 2017, Pages 26–41.
		\item T. Galibus, T. P. B. Vieira, E. P. de Freitas, R. Albuquerque, J. P. C. L. da Costa, R. T. de Sousa Jr, V. Krasnoproshin, A. Zaleski, H. Vissia, and G. del Galdo, \textit{Offline Mode for Corporate Mobile Client Security Architecture}. Mobile Networks and Applications, Springer, Mar 2017, Pages 1-17.
		\item K. H. C. Ramos, R. T. Sousa Jr, T. P. B. Vieira, and J. P. C. L. da Costa, \textit{DISCOVERING CRITICAL SUCCESS FACTORS FOR INFORMATION TECHNOLOGIES GOVERNANCE THROUGH BIBLIOMETRIC ANALYSIS OF RESEARCH PUBLICATIONS IN THIS DOMAIN}. Information (Yamaguchi), 2016
		\item K. H. C. Ramos, R. T. de Sousa Jr., T. P. B. Vieira, and J. P. C. L. da Costa, \textit{Identifying relevant IT governance critical success factors by means of bibliometric analysis}. 7th International Conference on Information, November 2015, Taipei, Taiwan.
		\item K. H. C. Ramos, T. P. B. Vieira, J. P. C. L. da Costa, and R. T. Sousa Jr., \textit{ANÁLISE MULTIDIMENSIONAL DE FATORES CRÍTICOS DE SUCESSO EM GOVERNANÇA DE TI NA ADMINISTRAÇÃO PÚBLICA FEDERAL À LUZ DOS DADOS DE CONTROLE EXTERNO}. in Proc. 12th International Conference on Management of Technology and Information Systems (CONTECSI), 2015, São Paulo, Brazil.
	\end{enumerate}
\end{enumerate}

>>>>

\begin{enumerate}
	\item We proposed an approach based on eigen similarity analysis for extracting detailed information about accurate time and network ports under network attack, and evaluated the accuracy and performance of the proposed framework applied to a experimental scenario and to the DARPA 1998 dataset;
	\item We discussed the computational complexity of the proposed framework and evaluated the required processing time for tested scenarios;
	\item We proposed an architechture and techniques for offline behavioral analysis of a corporate mobile client security architecture;
	\item We discussed the processing time of the proposed framework for mobile devices;
	\item We proposed an tensor-based dictionary learning approach for fraud detection in mobile payment transactions;
	\item We published the following papers reporting our results:
	\begin{enumerate}
		\item T. P. B. Vieira, D. F. Ten\'orio, J. P. C. L. da Costa, E. P. de Freitas, G. Del Galdo, and R. T. de Sousa J\'unior, \textit{Model Order Selection and Eigen Similarity based Framework for Detection and Identication of Network Attacks}. Journal of Networking and Computer Applications (JNCA), Vol 90, Jul 2017, Pages 26–41 \cite{vieira2017model}.
		\item T. Galibus, T. P. B. Vieira, E. P. de Freitas, R. Albuquerque, J. P. C. L. da Costa, R. T. de Sousa Jr, V. Krasnoproshin, A. Zaleski, H. Vissia, and G. del Galdo, \textit{Offline Mode for Corporate Mobile Client Security Architecture}. Mobile Networks and Applications, Springer, Mar 2017, Pages 1-17 \cite{galibus2017offline}.
		\item K. H. C. Ramos, R. T. Sousa Jr, T. P. B. Vieira, and J. P. C. L. da Costa, \textit{Discovering Critical Success Factors for Information Technologies Governance through Bibliometric Analysis of Research Publications in This Domain}. Information (Yamaguchi), 2016 \cite{ramos2016information}.
		\item K. H. C. Ramos, T. P. B. Vieira, J. P. C. L. da Costa, and R. T. Sousa Jr., \textit{ANÁLISE MULTIDIMENSIONAL DE FATORES CRÍTICOS DE SUCESSO EM GOVERNANÇA DE TI NA ADMINISTRAÇÃO PÚBLICA FEDERAL À LUZ DOS DADOS DE CONTROLE EXTERNO}. in Proc. 12th International Conference on Management of Technology and Information Systems (CONTECSI), 2015, São Paulo, Brazil \cite{}.
	\end{enumerate}
\end{enumerate}
